For Induction-Induction, Induction is Enough

### 2019-11-11 paper/paper.tex
stuff

\todo{András: overall todos: introduction, section 2 examples, intro to section 3, future work, maybe changing big Sigma notation to (x : A) x B notation (or changing the other way?)n}

@@

\todo{Without UIP, without funext,
for QIITs (in the setoid model).}

>>>>

\todo{András: overall todos: introduction, section 2 examples, intro to section 3, future work finish, maybe changing big Sigma notation to (x : A) x B notation (or changing the other way?)n}

@@

\subsection{Construction without UIP and function extensionality}
\todo{Without UIP, without funext,
for QIITs (in the setoid model).}
